### 2023-04-20 source/paper/tables.tex
Just in case again...

\import{../../output/tables/}{DiD_2010_high_low.tex}
\begin{footnotesize}
  \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 2008. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
\end{footnotesize}

\import{../../output/tables/}{DiD_2010_high_low_cont.tex}
\begin{footnotesize}
  \noindent Note: Treatment is continuous. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}
\clearpage

@@

\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. The controls used include age, age-squared, Latino ethnicity, and binned family income. The sample is defined as Black males and females aged 18-24 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}

@@

\import{../../output/tables/ddd}{ddd_1986_ab.tex}
\begin{footnotesize}
  \noindent Note: CPS data from 1984-1992.
  The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
\end{footnotesize}

\import{../../output/tables/ddd}{ddd_1986_jb.tex}

\import{../../output/tables/ddd}{ddd_2010_ab.tex}

\import{../../output/tables/ddd}{ddd_2010_jb.tex}
\clearpage

>>>>

@@

\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
\begin{footnotesize}
  \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. The controls used include age, age-squared, Latino ethnicity, and binned family income. The sample is defined as Black males and females aged 18-24 in 2010 who were not incarcerated at the time of the survey.
\end{footnotesize}
\clearpage

@@
